Left-linear rewriting in adhesive categories

### 2024-04-22 concur/fusione.tex
sempre typos

  \vspace{.1cm}
  \noindent
  \parbox{10cm}{\hspace{15pt}Given two objects $G$ and $H$ and a rule
    $\rho=(l,r)$ in $\R$, a \emph{direct derivation $\mathscr{D}$ from
      $G$ to $H$ applying rule $\rho$} is a diagram as the one
    aside, in which both squares are pushouts. The arrow $m$ is called
    the \emph{match} of the derivation, while $h$ is its
    \emph{back-match}.  We denote a direct derivation $\dder{D}$
    from $G$ to $H$ as $\dder{D}\colon G\Mapsto H$. }
  \parbox{3cm}{$\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l}
      \ar[r]^{r} & R \ar[d]^{h}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}&
      H}$}
\end{definition}

@@

  If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and
  $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with associated sequence of rules
  $r(\der{D})=\{\rho_i\}_{i=0}^n$ and
  $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation}
  between $(\der{D}, \alpha, \omega)$ and
  $(\der{D}', \alpha', \omega')$ is a permutation
  $\sigma\colon [0,n]\to [0,n]$ such that, for every $i\in [0,n]$,
  $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a
  \emph{mediating isomorphism}
  $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the
  following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are,
  respectively, the matches and back-matches of $\dder{D}_i$ and
  $\dder{D}'_i$.

@@

	A \emph{consistent} permutation between two derivations $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and
	$\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with associated sequence of rules
	$r(\der{D})=\{\rho_i\}_{i=0}^n$ is a permutation
	$\sigma\colon [0,n]\to [0,n]$ such that, for every $i\in [0,n]$,
	$\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a
	\emph{mediating isomorphism}
	$\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the
	following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are,
	respectively, the matches and back-matches of $\dder{D}_i$ and
	$\dder{D}'_i$.
	\[
	\xymatrix{
		G_0 \ar[r]^{\iota'_{G'_0}} \ar[d]_{\iota_{G_0}}& \lpro \der{D}' \rpro &L_i\ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}}
		&\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i}
		\ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}}
		&\tpro{D} \ar[d]^{\xi_\sigma} \\\tpro{D} \ar[ur]_{\xi_\sigma}&&G'_{\sigma(i)}
		\ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro&
		G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro
		\der{D}' \rpro}
	\]
\end{definition}

@@

  \begin{figure}[t]
    \input{Figure/derF.tex}    
    \caption{A derivation $\der{F}$.} 
    \label{fi:derF}
  \end{figure}

  \begin{figure}[t]
    \input{Figure/derF1.tex}    
    \caption{A derivation $\der{F}'$.} 
    \label{fi:derF1}
  \end{figure}
\end{example}

@@

	Since $f_1$ is mono then $i_0=j_0$. For every $v$ with depth $0$ we have
	\[g_{0,v}\circ i_{1,v}=h_{0,v}=g_{0,v}\circ j_{1,v}\]
	which entails $i_{1,v}=j_{1,v}$. Let now $v$ be a vertex with depth greater than $0$, and take $x\in L_1(v)$. By definition, we have $p:w\to v$ and $y\in L_{1}(w)$  such that $\dph(w)=0$ and $L(p)(y)=x$. By naturality we have
	\[i_{1,v}(x)=i_{1,v}(L(p)(y))=L(p)(i_{1, w}(y))=L(p)(j_{1, w}(y))=j_{1,v}(L(p)(y))=j_{1,v}(x)\]
	From this we can deduce that $i_{1,v}=j_{1,v}$, as wanted.
\end{proof}

@@

	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and
	$\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with associated sequence of rules
	$r(\der{D})=\{\rho_i\}_{i=0}^n$ and
	$r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation}
	between $(\der{D}, \alpha, \omega)$ and
	$(\der{D}', \alpha', \omega')$ is a permutation
	$\sigma\colon [0,n]\to [0,n]$ such that, for every $i\in [0,n]$,
	$\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a
	\emph{mediating isomorphism}
	$\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the
	following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are,
	respectively, the matches and back-matches of $\dder{D}_i$ and
	$\dder{D}'_i$

>>>>

  \vspace{.1cm}
  \noindent
  \parbox{10cm}{\hspace{15pt}Given two objects $G$ and $H$ and a rule
    $\rho=(l,r)$ in $\R$, a \emph{direct derivation $\mathscr{D}$ from
      $G$ to $H$ applying rule $\rho$} is a diagram as the one
    aside, in which both squares are pushouts. The arrow $m$ is called
    the \emph{match} of the derivation, while $h$ is its
    \emph{co-match}.  We denote a direct derivation $\dder{D}$
    from $G$ to $H$ as $\dder{D}\colon G\Mapsto H$. }
  \parbox{3cm}{$\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l}
      \ar[r]^{r} & R \ar[d]^{h}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}&
      H}$}
\end{definition}

@@

  If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and
  $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with associated sequence of rules
  $r(\der{D})=\{\rho_i\}_{i=0}^n$ and
  $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation}
  between $(\der{D}, \alpha, \omega)$ and
  $(\der{D}', \alpha', \omega')$ is a permutation
  $\sigma\colon [0,n]\to [0,n]$ such that, for every $i\in [0,n]$,
  $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a
  \emph{mediating isomorphism}
  $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the
  following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are,
  respectively, the matches and co-matches of $\dder{D}_i$ and
  $\dder{D}'_i$.

@@

	A \emph{consistent} permutation between two derivations $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and
	$\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with associated sequence of rules
	$r(\der{D})=\{\rho_i\}_{i=0}^n$ is a permutation
	$\sigma\colon [0,n]\to [0,n]$ such that, for every $i\in [0,n]$,
	$\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a
	\emph{mediating isomorphism}
	$\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the
	following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are,
	respectively, the matches and co-matches of $\dder{D}_i$ and
	$\dder{D}'_i$.
	\[
	\xymatrix{
		G_0 \ar[r]^{\iota'_{G'_0}} \ar[d]_{\iota_{G_0}}& \lpro \der{D}' \rpro &L_i\ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}}
		&\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i}
		\ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}}
		&\tpro{D} \ar[d]^{\xi_\sigma} \\\tpro{D} \ar[ur]_{\xi_\sigma}&&G'_{\sigma(i)}
		\ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro&
		G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro
		\der{D}' \rpro}
	\]
\end{definition}

@@

  \begin{figure}[t]
    \input{Figure/derF.tex}    
    \caption{The derivation $\der{F}$.} 
    \label{fi:derF}
  \end{figure}

  \begin{figure}[t]
    \input{Figure/derF1.tex}    
    \caption{The derivation $\der{F}'$.} 
    \label{fi:derF1}
  \end{figure}
\end{example}

@@

	Since $f_1$ is mono then $i_0=j_0$. For every $v$ with depth $0$ we have
	\[g_{0,v}\circ i_{1,v}=m_{1,v}=g_{0,v}\circ j_{1,v}\]
	which entails $i_{1,v}=j_{1,v}$. Let now $v$ be a vertex with depth greater than $0$, and take $x\in L_1(v)$. By definition, we have $p:w\to v$ and $y\in L_{1}(w)$  such that $\dph(w)=0$ and $L(p)(y)=x$. By naturality we have
	\[i_{1,v}(x)=i_{1,v}(L(p)(y))=L(p)(i_{1, w}(y))=L(p)(j_{1, w}(y))=j_{1,v}(L(p)(y))=j_{1,v}(x)\]
	From this we can deduce that $i_{1,v}=j_{1,v}$, as wanted.
\end{proof}

@@

	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and
	$\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with associated sequence of rules
	$r(\der{D})=\{\rho_i\}_{i=0}^n$ and
	$r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation}
	between $(\der{D}, \alpha, \omega)$ and
	$(\der{D}', \alpha', \omega')$ is a permutation
	$\sigma\colon [0,n]\to [0,n]$ such that, for every $i\in [0,n]$,
	$\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a
	\emph{mediating isomorphism}
	$\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the
	following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are,
	respectively, the matches and co-matches of $\dder{D}_i$ and
	$\dder{D}'_i$
